### 2025-09-25 paper/sec/conclusion.tex
Tweak concl.

Future work includes reducing reliance on predefined helper functions
such as \kw{growShrink} and \kw{trendWord}. While these provide a uniform
framework, we aim to enable the system to operate in their absence,
for instance by turning ``definition not found'' errors into augmented
prompts that trigger automatic generation of missing definitions. We
also plan to broaden the scope of supported artifacts, extending
interpretation to visualisations and intermediate datasets derived
from cleansing or aggregation, and to cover additional idioms such as
cardinals, multiplicatives, rounding, and graded adjectives.

@@

%Providing helper functions such as \kw{growShrink} and \kw{trendWord} as a predefined library is in some ways
%beneficial because they offer a uniform framework for interpreting a given scholarly document. We would also
%like make the system able to operate in the absence of these, perhaps adding a loopback condition to turn
%``Definition not found'' errors into an augmented prompt to generate the appropriate definition.

>>>>

Future work includes reducing reliance on predefined helper functions such as \kw{growShrink} and
\kw{trendWord}. While there is an advantage in using a predefined set of helpers (in that they offer a uniform
framework for interpreting a given scholarly document), we also aim to enable the system to operate in their
absence, for instance by turning ``definition not found'' errors into augmented prompts that trigger automatic
generation of missing definitions. We also plan to broaden the scope of supported artifacts, extending
interpretation to visualisations and intermediate datasets derived from cleansing or aggregation, and to cover
additional idioms such as cardinals, multiplicatives, rounding, and graded adjectives.

@@
